Predicting the conformational preferences of proteins using a physics-based free energy method

### 2013-04-24 Paper/paper.tex

   \item  The free energy of confining the ensemble (A or B) to a microstate (A* or B*) is
       calculated. This is done by gradually applying larger and larger
       harmonic restraints on all the atoms of the biomolecule. This is done by running 21 molecular dynamics simulation 
       (20 ns long each), where the harmonic restraint force constant was scaled from 0.00005
       \Alberto{units??}
       (mostly free) to 81.92 (frozen in one microstate). In this final restrained state, the
       rotational contribution to the free energy is frozen out
       and the only remaining contribution is the vibrational part. The free energy for this step is
       estimated from the fluctuations around
       the reference structure using a numerical
       approach developed by Tyka et. al. \cite{Tyka2006}. The confinement free energy calculated in
       this way is recorded as 
       $\Delta G_{A,A*}$ and $\Delta G_{B,B*}$ as shown in Figure~\ref{fig:method}.

@@

\bibitem{Wang2011}
Wang, Q.; Vantasin, K.; Xu, D.; Shang, Y. MUFOLD-WQA: A new selective consensus method for quality assessment in protein structure prediction.
Proteins, 2011, 79: 185–195.

>>>>

   \item  The free energy of confining the ensemble (A or B) to a microstate (A* or B*) is
       calculated. This is done by gradually applying larger and larger
       harmonic restraints on all the atoms of the biomolecule. This is done by running 21 molecular dynamics simulation 
       (20 ns long each), where the harmonic restraint force constant was scaled from 0.00005
       Kcal/Mol 
       (mostly free) to 81.92 iKcal/Mol (frozen in one microstate). In this final restrained state, the
       rotational contribution to the free energy is frozen out
       and the only remaining contribution is the vibrational part. The free energy for this step is
       estimated from the fluctuations around
       the reference structure using a numerical
       approach developed by Tyka et. al. \cite{Tyka2006}. The confinement free energy calculated in
       this way is recorded as 
       $\Delta G_{A,A*}$ and $\Delta G_{B,B*}$ as shown in Figure~\ref{fig:method}.

@@

\bibitem{Wang2011}
Wang, Q.; Vantasin, K.; Xu, D.; Shang, Y. MUFOLD-WQA: A new selective consensus method for quality assessment in protein structure prediction.
Proteins, 2011, 79: 185-195.
